### 2014-11-10 Arvind.tex
Pass through Respecifying

Our final theorem in this paper establishes that a particular complex hardware
system implements sequential consistency (SC) properly.  We state the theorem
in terms of the trace refinement relation $\sqsubseteq$ developed in the prior
section.  Therefore, we need to define an LTS embodying SC.  The simpler this
system, the better.  We do not need to worry about its performance properties,
since we will prove that an optimized system remains faithful to it.

@@

Note that, in this setting, an operational specification like the LTS
for SC is precisely the right characterization of \emph{full functional
  correctness} for a hardware design, much as a
precondition-postcondition pair does that job in a partial-correctness
Hoare logic.  Our SC LTS fully constrains observable behavior of a
system to remain consistent with simple interleaving.  Similar
operational models are possible as top-level specifications for
systems following weaker memory models, by giving the LTS for the \emph{Local
Buffer} component and composing the three components simultaneously.

@@

The simple memory defined earlier in Figure~\ref{$M_m$} is meant to be composed with P$_{\text{ref}}$
processors.  %The input-output interface of this memory $M_m$ is largely what
%one would expect from the P$_{\text{ref}}$ definition. 
%However, in anticipation of the
%more complex processor we will define later, we add requests and responses for
%\emph{speculative loads}.  These are load operations that a processor may
a%ttempt, before it knows that the program will actually need the result.  Many
s%peculative loads from a single processor may be in flight at once, improving
p%erformance via parallelism. 
A request to memory like $(t, \ld, a)$ asks
for the value of memory cell $a$, associating a \emph{tag} $t$ that the
processor can use to match responses to requests.  Those responses take the
form $(t, \ld, v)$, giving the value $v$ of the requested memory address.

@@

\paragraph{The final theorem and the proof plan:} 
In this section we divided a multiprocessor system into two rather simple
components, processor represented by $P_\text{ref}$ and memory represented by
$M_m$. In the following two sections we will develop more complex, optimized
versions of each piece and prove their correctness, that is, $P_\text{so}$, the
speculative out-of-order processor, is sound with respect to $P_\text{ref}$ and
$M_c$, the cache memory, is sound with respect to $M_m$. In proving the
soundness of $P_\text{so}$ with respect to $P_\text{ref}$, we need to focus
only on non-speculative communications. The main theorem we are after is to
show that P$^n_\text{so}+ M_c$ is SC, by showing that it is sound with respect
to P$^n_\text{ref}+ M_m$. Figure~\ref{proofs} gives the overall proof structure
that we will employ.

>>>>

Our final theorem in this paper establishes that a particular complex hardware
system implements sequential consistency (SC) properly.  We state the theorem
in terms of the trace refinement relation $\sqsubseteq$ developed in
Section~\ref{sec:lts}.
Therefore, we need to define an LTS embodying SC.  The simpler this
system, the better.  We do not need to worry about its performance properties,
since we will prove that an optimized system remains faithful to it.

@@

Note that, in this setting, an operational specification like the LTS
for SC is precisely the right characterization of \emph{full functional
  correctness} for a hardware design, much as a
precondition-postcondition pair does that job in a partial-correctness
Hoare logic.  Our SC LTS fully constrains observable behavior of a
system to remain consistent with simple interleaving.  Similar
operational models are possible as top-level specifications for
systems following weaker memory models, by giving the LTS for the \emph{local
buffer} component and composing the three components simultaneously.

@@

The simple memory defined earlier in Figure~\ref{$M_m$} is meant to be composed with P$_{\text{ref}}$
processors.  %The input-output interface of this memory $M_m$ is largely what
%one would expect from the P$_{\text{ref}}$ definition. 
%However, in anticipation of the
%more complex processor we will define later, we add requests and responses for
%\emph{speculative loads}.  These are load operations that a processor may
%attempt, before it knows that the program will actually need the result.  Many
%speculative loads from a single processor may be in flight at once, improving
%performance via parallelism. 
A request to memory like $(t, \ld, a)$ asks
for the value of memory cell $a$, associating a \emph{tag} $t$ that the
processor can use to match responses to requests.  Those responses take the
form $(t, \ld, v)$, giving the value $v$ of the requested memory address.

@@

\paragraph{The final theorem and the proof plan:} 
In this section we divided a multiprocessor system into two rather simple
components, processor represented by $P_\text{ref}$ and memory represented by
$M_m$. In the following two sections we will develop more complex, optimized
versions of each piece and prove their correctness.  That is, we define $P_\text{so}$, the
speculative out-of-order processor, and prove it sound with respect to $P_\text{ref}$;
and we define $M_c$, the cache memory, and prove it sound with respect to $M_m$. In proving the
soundness of $P_\text{so}$ with respect to $P_\text{ref}$, we need to focus
only on nonspeculative communications. The main theorem we are after is to
show that P$^n_\text{so}+ M_c$ is SC, by showing that it is sound with respect
to P$^n_\text{ref}+ M_m$. Figure~\ref{proofs} gives the overall proof structure
that we will employ.
